Trends of SDR in Thessaloniki

### 2023-10-08 Article.Rmd
Commit 2023-10-08 20:11

```{r cusum, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR for the three different sky conditions.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCuSum-1.png",    # ALL sky
    "./images/CumulativeDailyCuSum-5.png",    # CLEAR sky
    "./images/CumulativeDailyCuSum-9.png"))   # Cloud sky
```

@@

>>>>

```{r cusum, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCuSum-1.png",    # ALL sky
    "./images/CumulativeDailyCuSum-5.png",    # CLEAR sky
    "./images/CumulativeDailyCuSum-9.png"))   # Cloud sky
```

```{r cusummonth, echo = FALSE, fig.cap='Running cumulative sum plots of the monthly SDR.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeMonthlyCuSum-1.png",    # ALL sky
    "./images/CumulativeMonthlyCuSum-5.png",    # CLEAR sky
    "./images/CumulativeMonthlyCuSum-9.png"))   # Cloud sky
```

@@

<!-- ```{r cusumnotrendmonthly, echo = FALSE, fig.cap='Running cumulative sum plots of the monthly SDR after removing the long term trend from the monthly values, for the three different sky conditions.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeMonthlyCuSum",    # ALL sky -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-5.png",    # CLEAR sky -->
<!--     "./images/CumulativeMonthlyCuSumNOtrend-9.png"))   # Cloud sky -->
<!-- ``` -->
